My Findings

### 2024-02-09 Findings (Shared Folder)/Chapters/modelAttempts.tex
new analysis added

\subsubsection*{Effect of $\gamma$}

>>>>

\subsubsection*{Effect of $\gamma$}
$\gamma$ is basically determining the slope of the $\dot{\rho}=0$ nullcline. The higher the value of $\gamma$ the more steeper is the slop. Thus changing the values of $\gamma$, the equilibrium point $p^0_2$ will move up or down on the $\dot{n}=0$ nullcline. The sign of $\alpha$ determines the way $p^0_2$ changes. The following figure summarizes the results for the argument above.

\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{images/effectOfGamma.png} % first image
\end{figure}
\FloatBarrier

\subsubsection*{Effect of $\beta$}
Determining the effect of the parameter $\beta$ is not as straight forward as the other two parameters as it appears in both ODEs. However, we can plot the parameterized curve of $p^0_2(\beta)$ using (E.1.1) to see the effect of $\beta$ on the equilibrium point. The following figure summarizes the effect of $\beta$ on $p^0_2$.

\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{images/EffectOfBeta.png} % first image
\end{figure}
\FloatBarrier
